---
title: "WeCare Medical Record Data — Descriptive Statistics"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
    toc_float: true
    number_sections: true
params:
  xlsx_path: /Users/jaimiechin/Desktop/WeCare_Project_Edit/data/raw/medical_records_02042026.xlsx
  export_csv: true
  csv_dir: /Users/jaimiechin/Desktop/WeCare_Project_Edit/data/out/
  sample_roster_csv: data/sample_roster.csv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(purrr)
library(readr)
library(readxl)

`%||%` <- function(x, y) if (is.null(x) || length(x) == 0) y else x
```

# 1) Import/Export
```{r export-xlsx-to-csv}
xlsx_path <- params$xlsx_path
csv_dir   <- params$csv_dir

sheets <- excel_sheets(xlsx_path)

if (isTRUE(params$export_csv)) {
  dir.create(csv_dir, showWarnings = FALSE, recursive = TRUE)

  walk(sheets, function(sh) {
    df <- read_excel(xlsx_path, sheet = sh, guess_max = 50000)
    out_name <- str_replace_all(sh, "[^A-Za-z0-9_\\-]+", "_")
    out_path <- file.path(csv_dir, paste0(out_name, ".csv"))
    write_csv(df, out_path, na = "")
  })
}

sheets
```

# 2) User Inputs
```{r user-inputs, message=FALSE, warning=FALSE}
# ========================= USER INPUTS ======================

# Report mode:
# - "weekly"  = Monday-Sunday periods based on DATES_INPUT
# - "monthly" = calendar months based on DATES_INPUT
# - "DSMB"    = DSMB sections only, uses DATA_LOCK
REPORT_MODE <- "weekly"

# Which dates to include
# Weekly: any date inside the week is fine
# Monthly: any date inside the month is fine
DATES_INPUT <- as.Date(c("2026-03-02", "2026-03-09", "2026-03-16", "2026-03-23", "2026-03-30", "2026-04-08", "2026-04-13"))

# Required report cutoff for DSMB and cumulative summaries
DATA_LOCK <- as.Date("2026-04-13")

# Optional render toggles
SHOW_REGULAR_AE_SAE_TABLES <- TRUE
SHOW_DSMB                  <- TRUE
```

# 3) Import Medical Data 
```{r load-sheets}
# ---- CHANGE THESE if needed ----
matched_participants_sheet <- sheets[1]
encounters_sheet           <- sheets[2]

participants <- read_excel(xlsx_path, sheet = matched_participants_sheet, guess_max = 50000)
encounters   <- read_excel(xlsx_path, sheet = encounters_sheet, guess_max = 50000)

list(
  participants_cols = names(participants),
  encounters_cols   = names(encounters)
)
```

# 2) Standardize Core Tables
```{r standardize}
participants_std <- participants %>%
  transmute(
    participant_id      = as.character(PARTICIPANT_ID),
    original_ehr_pt_id  = as.character(ORIGINAL_EHR_PT_ID),
    empi                = as.character(EMPI),
    match_comment       = as.character(MATCH_COMMENT),
    last_name           = as.character(LAST_NAME),
    first_name          = as.character(FIRST_NAME),
    name                = str_squish(paste(first_name, last_name)),
    dob                 = as_date(DOB),
    gender_at_birth     = as.character(GENDER_AT_BIRTH),
    enrollment_date     = as_date(DATE_OF_ENROLLMENT)
  )

encounters_std <- encounters %>%
  transmute(
    participant_id       = as.character(PARTICIPANT_ID),
    visit_date           = as_date(ENC_DATE),
    csn                  = as.character(CSN),
    facility             = as.character(FACILITY),
    department           = as.character(DEPARTMENT),
    specialty            = as.character(SPECIALTY),
    patient_class        = as.character(PATIENT_CLASS),
    encounter_type       = as.character(ENCOUNTER_TYPE),
    provider_name        = as.character(PROVIDER_NAME),
    primary_ins_type     = as.character(PRIMARY_INSURANCE_TYPE),
    payor_name           = as.character(PAYOR_NAME),
    subscriber_id        = as.character(SUBSCRIBER_ID),
    diagnoses_raw        = as.character(DIAGNOSES),
    procedures_raw       = as.character(PROCEDURES)
  )
```

# 2B) Apply 12-month-from-enrollment restriction (use these downstream)
```{r apply-12m-window}
# Define the allowed MR window per participant:
# - start: enrollment_date
# - end: enrollment_date + 12 months (exclusive)
#   (Using exclusive end avoids edge-case double counting if you later chain windows)
participants_window <- participants_std %>%
  mutate(
    window_start = enrollment_date,
    window_end   = enrollment_date %m+% months(12)   # exclusive upper bound
  )

# Encounters restricted to within 12 months of enrollment
encounters_std_12m <- encounters_std %>%
  left_join(
    participants_window %>% select(participant_id, window_start, window_end),
    by = "participant_id"
  ) %>%
  mutate(
    in_12m_window =
      !is.na(window_start) &
      !is.na(window_end) &
      !is.na(visit_date) &
      visit_date >= window_start &
      visit_date <  window_end
  ) %>%
  filter(in_12m_window) %>%
  select(-in_12m_window)

# Optional: participants who have at least one encounter in-window (sometimes useful)
participants_std_12m <- participants_std %>%
  semi_join(encounters_std_12m %>% distinct(participant_id), by = "participant_id")

# Quick QC counts (overall vs windowed)
tibble(
  n_participants_total        = n_distinct(participants_std$participant_id),
  n_participants_with_any_enc = n_distinct(encounters_std$participant_id),
  n_encounters_total          = nrow(encounters_std),
  n_participants_with_enc_12m = n_distinct(encounters_std_12m$participant_id),
  n_encounters_12m            = nrow(encounters_std_12m)
)
```

# Shared Helpers for Old + New Tables
```{r shared-helpers, message=FALSE, warning=FALSE}
# ============================================================
# Shared helpers used by both old tables and new reporting
# ============================================================

# -----------------------------
# Roster linkage
# -----------------------------
roster_path <- "/Users/jaimiechin/Library/CloudStorage/Box-Box/WeCare (Michael Wu)/Data/cleaned/New ETL Output/dat_merged.csv"

dat_merged_raw <- read_csv(roster_path, show_col_types = FALSE)

pick_first_existing <- function(data, candidates) {
  hits <- candidates[candidates %in% names(data)]
  if (length(hits) == 0) return(NA_character_)
  hits[1]
}

visit_3m_col <- pick_first_existing(
  dat_merged_raw,
  c("visit_date_3m", "visit_3m_date", "date_3m_visit", "fu_3m_visit_date")
)

visit_6m_col <- pick_first_existing(
  dat_merged_raw,
  c("visit_date_6m", "visit_6m_date", "date_6m_visit", "fu_6m_visit_date")
)

roster_key <- dat_merged_raw %>%
  transmute(
    participant_id = as.character(record_id),
    site_id = as.character(site_id),
    treatment = suppressWarnings(as.integer(treatment)),
    visit_date_3m = if (!is.na(visit_3m_col)) as.Date(.data[[visit_3m_col]]) else as.Date(NA),
    visit_date_6m = if (!is.na(visit_6m_col)) as.Date(.data[[visit_6m_col]]) else as.Date(NA)
  ) %>%
  mutate(
    site = case_when(
      site_id == "H" ~ "Harlem",
      site_id == "K" ~ "Kings",
      TRUE ~ "Unknown"
    ),
    tx_group = case_when(
      treatment == 1 ~ "TX",
      treatment == 0 ~ "Control",
      TRUE ~ "Unknown"
    ),
    site_full = case_when(
      site_id == "H" ~ "Harlem Hospital",
      site_id == "K" ~ "Kings County Hospital",
      TRUE ~ "Unknown"
    )
  )

# Quick QC
list(
  visit_3m_col_found = visit_3m_col,
  visit_6m_col_found = visit_6m_col,
  roster_key_cols = names(roster_key)
)

# -----------------------------
# Period helpers
# -----------------------------
get_week_start <- function(x) floor_date(as.Date(x), unit = "week", week_start = 1)
get_week_end   <- function(x) get_week_start(x) + days(6)

get_month_start <- function(x) floor_date(as.Date(x), unit = "month")
get_month_end   <- function(x) ceiling_date(as.Date(x), unit = "month") - days(1)

build_periods <- function(dates_input, report_mode = c("weekly", "monthly", "DSMB")) {
  report_mode <- match.arg(report_mode)

  if (report_mode == "weekly") {
    tibble(input_date = as.Date(dates_input)) %>%
      mutate(
        period_start = get_week_start(input_date),
        period_end   = get_week_end(input_date),
        period_label = paste0(format(period_start, "%Y-%m-%d"), " to ", format(period_end, "%Y-%m-%d"))
      ) %>%
      distinct(period_start, period_end, period_label) %>%
      arrange(period_start)
  } else if (report_mode == "monthly") {
    tibble(input_date = as.Date(dates_input)) %>%
      mutate(
        period_start = get_month_start(input_date),
        period_end   = get_month_end(input_date),
        period_label = format(period_start, "%Y-%m")
      ) %>%
      distinct(period_start, period_end, period_label) %>%
      arrange(period_start)
  } else {
    tibble(
      period_start = as.Date(NA),
      period_end   = DATA_LOCK,
      period_label = paste0("Through ", DATA_LOCK)
    )
  }
}

periods_tbl <- build_periods(DATES_INPUT, REPORT_MODE)

# -----------------------------
# ICD helpers
# -----------------------------
clean_icd10 <- function(x) {
  x %>%
    as.character() %>%
    str_trim() %>%
    str_to_upper() %>%
    str_replace_all("\\.", "") %>%
    na_if("")
}

extract_icd10_from_diagnoses_raw <- function(x) {
  str_extract_all(as.character(x), "\\(([A-Za-z][A-Za-z0-9\\.]*)\\)") %>%
    lapply(function(v) str_replace_all(v, "[()]", "")) %>%
    lapply(function(v) v[v != ""])
}

# Alias used by one of your old chunks
extract_icd10_parentheses <- function(x) {
  out <- extract_icd10_from_diagnoses_raw(x)
  purrr::map(out, ~clean_icd10(.x))
}

is_suicidal_ideation <- function(icd_clean) {
  str_detect(icd_clean, "^R45851$")
}

is_suicide_attempt_code <- function(icd_clean) {
  str_detect(icd_clean, "^T1491$")
}

is_intentional_self_harm_or_attempt <- function(icd_clean) {
  starts_T36_T65 <- str_detect(icd_clean, "^T(3[6-9]|[4-5][0-9]|6[0-5])")
  intent_digit_5_or_6_is_2 <- (str_sub(icd_clean, 5, 5) == "2") | (str_sub(icd_clean, 6, 6) == "2")
  poisoning_flag <- starts_T36_T65 & intent_digit_5_or_6_is_2

  t71_flag <- str_detect(icd_clean, "^T71") &
    ((str_sub(icd_clean, 6, 6) == "2") | (str_sub(icd_clean, 5, 5) == "2"))

  x71_x82_flag <- str_detect(icd_clean, "^(X71|X72|X73|X74|X75|X76|X77|X78|X79|X80|X81|X82)")
  x83_0_flag   <- str_detect(icd_clean, "^X830")
  x83_other    <- str_detect(icd_clean, "^(X831|X832|X838)")
  t1491_flag   <- str_detect(icd_clean, "^T1491")

  poisoning_flag | t71_flag | x71_x82_flag | x83_0_flag | x83_other | t1491_flag
}

is_death_code <- function(icd_clean) {
  str_detect(icd_clean, "^R99$|^I46|^I469|^Y339|^Y34|^X599|^X59")
}

# -----------------------------
# Study-bucket helper
# -----------------------------
assign_study_bucket <- function(visit_date, enrollment_date, visit_date_3m, visit_date_6m) {
  case_when(
    !is.na(visit_date) & !is.na(enrollment_date) & visit_date == enrollment_date ~ "At baseline",
    !is.na(visit_date) & !is.na(enrollment_date) & !is.na(visit_date_3m) &
      visit_date > enrollment_date & visit_date < visit_date_3m ~ "Baseline to <3m",
    !is.na(visit_date) & !is.na(visit_date_3m) & visit_date == visit_date_3m ~ "At 3m",
    !is.na(visit_date) & !is.na(visit_date_3m) & !is.na(visit_date_6m) &
      visit_date > visit_date_3m & visit_date < visit_date_6m ~ "3m to <6m",
    !is.na(visit_date) & !is.na(visit_date_6m) & visit_date == visit_date_6m ~ "At 6m",
    !is.na(visit_date) & !is.na(visit_date_6m) & visit_date > visit_date_6m ~ "After 6m",
    TRUE ~ "Unassigned"
  )
}

study_bucket_levels <- c(
  "At baseline",
  "Baseline to <3m",
  "At 3m",
  "3m to <6m",
  "At 6m",
  "After 6m",
  "Unassigned"
)

# -----------------------------
# Shared admission-proxy helper inputs
# -----------------------------
ip_classes_all <- c("Inpatient", "Observation", "Inpatient Psych", "Psych Observation")
psych_ip_classes <- c("Inpatient Psych", "Psych Observation")
ed_classes <- c("Emergency", "Psych Emergency")
```

# 3) Quick Coverage Counts
```{r quick-coverage-counts}
coverage_counts <- tibble(
  n_participants_table = n_distinct(participants_std$participant_id),
  n_participants_with_any_encounter = n_distinct(encounters_std$participant_id),
  n_encounters_total = nrow(encounters_std)
)

coverage_counts
```
The medical record extract includes *332 unique participants*, and all *332 have at least one recorded encounter* in the encounters table (consistent with everyone having an enrollment/baseline visit). Across these participants, there are *1,678 total encounters*

# 3B) Quick Coverage Counts (12-month restricted)
```{r quick-coverage-counts-12m}
coverage_counts_12m <- tibble(
  n_participants_table = n_distinct(participants_std$participant_id),
  n_participants_with_any_encounter_12m = n_distinct(encounters_std_12m$participant_id),
  n_encounters_total_12m = nrow(encounters_std_12m)
)

coverage_counts_12m
```

```{r qc-who-lost-all-encounters-in-12m}
ids_any <- encounters_std %>% distinct(participant_id)
ids_12m <- encounters_std_12m %>% distinct(participant_id)

anti_join(ids_any, ids_12m, by = "participant_id") %>%
  left_join(participants_std %>% select(participant_id, enrollment_date), by = "participant_id")
```

```{r qc-before-after-window}
lost_ids <- anti_join(
  encounters_std %>% distinct(participant_id),
  encounters_std_12m %>% distinct(participant_id),
  by = "participant_id"
)

encounters_std %>%
  semi_join(lost_ids, by = "participant_id") %>%
  left_join(
    participants_std %>%
      transmute(
        participant_id,
        enrollment_date,
        window_end = enrollment_date %m+% months(12)
      ),
    by = "participant_id"
  ) %>%
  mutate(
    timing = case_when(
      is.na(visit_date) ~ "missing visit_date",
      visit_date < enrollment_date ~ "pre-enrollment",
      visit_date >= window_end ~ ">=12 months after enrollment",
      TRUE ~ "in window (shouldn't happen)"
    )
  ) %>%
  count(timing)
```


# 4) Medicaid Summary & Line Lists 

```{r medicaid-summary}
is_medicaid <- function(primary_ins_type, payor_name) {
  x <- str_to_lower(paste(primary_ins_type %||% "", payor_name %||% ""))
  str_detect(x, "medicaid|medi-cal|chip|mmc")
}

encounters_medicaid <- encounters_std_12m %>%
  mutate(on_medicaid_encounter = is_medicaid(primary_ins_type, payor_name))

medicaid_person_level <- encounters_medicaid %>%
  group_by(participant_id) %>%
  summarise(on_medicaid = any(on_medicaid_encounter, na.rm = TRUE), .groups = "drop")

medicaid_summary <- medicaid_person_level %>%
  summarise(
    n_with_any_encounter = n(),
    n_medicaid = sum(on_medicaid, na.rm = TRUE),
    pct_medicaid = 100 * mean(on_medicaid, na.rm = TRUE)
  )

medicaid_summary
```
Using insurance fields on encounters (primary insurance type and payor name), *234 of 332 participants (70.48%)* are flagged as having Medicaid coverage on at least one recorded encounter (“ever Medicaid” in this extract).


```{r medicaid-line-list-all-encounters}
medicaid_encounter_list <- encounters_medicaid %>%
  filter(on_medicaid_encounter) %>%
  left_join(participants_std %>% select(participant_id, name, dob), by = "participant_id") %>%
  arrange(participant_id, visit_date) %>%
  select(
    participant_id, name, dob, visit_date,
    facility, department, patient_class, encounter_type,
    primary_ins_type, payor_name, subscriber_id
  )

medicaid_encounter_list
```

```{r medicaid-line-list-per-participant}
medicaid_participant_list <- medicaid_encounter_list %>%
  group_by(participant_id, name, dob) %>%
  summarise(
    last_medicaid_visit = max(visit_date, na.rm = TRUE),
    n_medicaid_encounters = n(),
    .groups = "drop"
  ) %>%
  arrange(desc(last_medicaid_visit))

medicaid_participant_list
```

```{r medicaid-summary-12m-strict}
# Strict Medicaid definition based on known value sets
is_medicaid_strict <- function(primary_ins_type, payor_name) {
  primary_ok <- primary_ins_type %in% c("Medicaid", "Medicaid Managed Care")
  payor_ok   <- payor_name %in% c("EMERGENCY MEDICAID", "NEW YORK MEDICAID")
  primary_ok | payor_ok
}

encounters_medicaid <- encounters_std_12m %>%
  mutate(
    primary_ins_type = str_squish(primary_ins_type),
    payor_name       = str_squish(payor_name),
    on_medicaid_encounter = is_medicaid_strict(primary_ins_type, payor_name)
  )

# Encounter-level totals
medicaid_encounter_summary <- encounters_medicaid %>%
  summarise(
    n_encounters_12m = n(),
    n_medicaid_encounters_12m = sum(on_medicaid_encounter, na.rm = TRUE),
    pct_encounters_medicaid_12m = 100 * mean(on_medicaid_encounter, na.rm = TRUE)
  )

# Participant-level totals
medicaid_person_level <- encounters_medicaid %>%
  group_by(participant_id) %>%
  summarise(
    any_medicaid_12m = any(on_medicaid_encounter, na.rm = TRUE),
    .groups = "drop"
  )

medicaid_participant_summary <- medicaid_person_level %>%
  summarise(
    n_participants_with_any_enc_12m = n(),
    n_participants_with_any_medicaid_12m = sum(any_medicaid_12m, na.rm = TRUE),
    pct_participants_with_any_medicaid_12m = 100 * mean(any_medicaid_12m, na.rm = TRUE)
  )

list(
  medicaid_encounter_summary = medicaid_encounter_summary,
  medicaid_participant_summary = medicaid_participant_summary
)
```

# 5) Post-Enrollment "hospital enocunters"
```{r}
enc_post_enroll <- encounters_std_12m %>%
  distinct(participant_id, csn, visit_date) %>%  # one row per unique encounter
  left_join(
    participants_std %>% select(participant_id, enrollment_date),
    by = "participant_id"
  ) %>%
  group_by(participant_id) %>%
  summarise(
    enrollment_date = first(enrollment_date),
    n_encounters = n(),
    first_encounter_date = min(visit_date, na.rm = TRUE),
    last_encounter_date  = max(visit_date, na.rm = TRUE),

    # count encounters strictly AFTER enrollment date
    n_post_enroll_encounters = sum(!is.na(visit_date) & !is.na(enrollment_date) & visit_date > enrollment_date),
    has_post_enroll_encounter = n_post_enroll_encounters >= 1,

    # earliest post-enrollment encounter date (if any)
    first_post_enroll_date = suppressWarnings(min(visit_date[!is.na(enrollment_date) & visit_date > enrollment_date], na.rm = TRUE)),
    .groups = "drop"
  ) %>%
  mutate(
    first_post_enroll_date = if_else(is.infinite(first_post_enroll_date), as.Date(NA), first_post_enroll_date)
  )

# Summary for Adam
enc_post_enroll %>%
  summarise(
    n_with_any_encounter = n(),
    n_with_post_enroll_encounter = sum(has_post_enroll_encounter, na.rm = TRUE),
    pct_with_post_enroll_encounter = 100 * mean(has_post_enroll_encounter, na.rm = TRUE)
  )
```

```{r post-enrollment-encounters-summary}
# Summary for Adam (now includes total post-enrollment encounters)
enc_post_enroll %>%
  summarise(
    n_with_any_encounter = n(),
    n_with_post_enroll_encounter = sum(has_post_enroll_encounter, na.rm = TRUE),
    pct_with_post_enroll_encounter = 100 * mean(has_post_enroll_encounter, na.rm = TRUE),

    # NEW: total number of encounters strictly after enrollment (across all participants)
    total_post_enroll_encounters = sum(n_post_enroll_encounters, na.rm = TRUE),

    # Optional: average # of post-enroll encounters per participant (overall)
    mean_post_enroll_encounters_all = mean(n_post_enroll_encounters, na.rm = TRUE),

    # Optional: average # of post-enroll encounters among those who had any
    mean_post_enroll_encounters_among_any = mean(n_post_enroll_encounters[has_post_enroll_encounter], na.rm = TRUE)
  )
```

```{r post-enrollment-encounters-distribution}
enc_post_enroll %>%
  count(n_post_enroll_encounters, name = "n_participants") %>%
  arrange(n_post_enroll_encounters)
```

# Encounter Level Table with Timing Flags
```{r encounter-timing-setup}
library(dplyr)
library(tidyr)

# CHANGE THIS to the actual column that represents "type"
TYPE_COL <- "encounter_type"  # e.g. "enc_type" or "visit_type" etc.

enc_timed <- encounters_std_12m %>%
  # keep only columns we need (add more if useful)
  select(participant_id, csn, visit_date, all_of(TYPE_COL)) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%  # one row per unique encounter
  left_join(
    participants_std %>% select(participant_id, enrollment_date),
    by = "participant_id"
  ) %>%
  mutate(
    timing = case_when(
      is.na(visit_date) | is.na(enrollment_date) ~ NA_character_,
      visit_date == enrollment_date ~ "enrollment_date",
      visit_date  > enrollment_date ~ "post_enroll",
      visit_date  < enrollment_date ~ "pre_enroll"
    ),
    encounter_type_clean = coalesce(.data[[TYPE_COL]], "Missing/Unknown")
  )
```

---

### 2) Breakdown: enrollment-date encounters vs post-enrollment encounters (by encounter type)

This gives you **n_encounters**, **n_participants**, and **% of encounters within that timing group**.

```{r encounter-type-breakdown-enroll-vs-post}
enc_type_breakdown <- enc_timed %>%
  filter(timing %in% c("enrollment_date", "post_enroll")) %>%
  group_by(timing, encounter_type_clean) %>%
  summarise(
    n_encounters = n(),
    n_participants = n_distinct(participant_id),
    .groups = "drop"
  ) %>%
  group_by(timing) %>%
  mutate(
    pct_encounters_within_timing = 100 * n_encounters / sum(n_encounters)
  ) %>%
  ungroup() %>%
  arrange(timing, desc(n_encounters))

enc_type_breakdown
```

---

### 3) Optional: Make it “report-ready” wide (enrollment vs post side-by-side)

```{r encounter-type-breakdown-wide}
enc_type_breakdown_wide <- enc_type_breakdown %>%
  select(timing, encounter_type_clean, n_encounters, n_participants, pct_encounters_within_timing) %>%
  pivot_wider(
    names_from = timing,
    values_from = c(n_encounters, n_participants, pct_encounters_within_timing),
    values_fill = 0
  ) %>%
  arrange(desc(n_encounters_post_enroll), desc(n_encounters_enrollment_date))

enc_type_breakdown_wide
```

---

### 4) Optional: Participant-level view (how many people had each type at enrollment vs post)

This is useful if you care more about **reach across participants** than raw encounter volume.

```{r encounter-type-participant-penetration}
enc_type_participant <- enc_timed %>%
  filter(timing %in% c("enrollment_date", "post_enroll")) %>%
  group_by(timing, encounter_type_clean) %>%
  summarise(
    n_participants = n_distinct(participant_id),
    .groups = "drop"
  ) %>%
  group_by(timing) %>%
  mutate(
    pct_participants_with_type = 100 * n_participants / n_distinct(enc_timed$participant_id)
  ) %>%
  ungroup() %>%
  arrange(timing, desc(n_participants))

enc_type_participant
```

---
```{r patient-class-breakdowns}
library(dplyr)
library(tidyr)

# If your column is not literally "patient_class", change it here:
CLASS_COL <- "patient_class"

patient_class_levels <- c(
  "Emergency",
  "Inpatient",
  "Inpatient Psych",
  "Observation",
  "Outpatient",
  "Psych Emergency",
  "Psych Observation",
  "Psych Series",
  "Therapies Series"
)

enc_timed_class <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, all_of(CLASS_COL)) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%  # one row per unique encounter
  left_join(
    participants_std %>% select(participant_id, enrollment_date),
    by = "participant_id"
  ) %>%
  mutate(
    timing = case_when(
      is.na(visit_date) | is.na(enrollment_date) ~ NA_character_,
      visit_date == enrollment_date ~ "enrollment_date",
      visit_date  > enrollment_date ~ "post_enroll",
      visit_date  < enrollment_date ~ "pre_enroll"
    ),
    patient_class_clean = case_when(
      is.na(.data[[CLASS_COL]]) ~ "Other/Unknown",
      .data[[CLASS_COL]] %in% patient_class_levels ~ .data[[CLASS_COL]],
      TRUE ~ "Other/Unknown"
    ),
    patient_class_clean = factor(
      patient_class_clean,
      levels = c(patient_class_levels, "Other/Unknown")
    )
  )

# 1) Long table: counts + % of encounters within timing (enrollment vs post)
patient_class_breakdown <- enc_timed_class %>%
  filter(timing %in% c("enrollment_date", "post_enroll")) %>%
  group_by(timing, patient_class_clean) %>%
  summarise(
    n_encounters = n(),
    n_participants = n_distinct(participant_id),
    .groups = "drop"
  ) %>%
  group_by(timing) %>%
  mutate(pct_encounters_within_timing = 100 * n_encounters / sum(n_encounters)) %>%
  ungroup() %>%
  arrange(timing, desc(n_encounters))

patient_class_breakdown

# 2) Wide table: side-by-side enrollment vs post
patient_class_breakdown_wide <- patient_class_breakdown %>%
  select(timing, patient_class_clean, n_encounters, n_participants, pct_encounters_within_timing) %>%
  pivot_wider(
    names_from = timing,
    values_from = c(n_encounters, n_participants, pct_encounters_within_timing),
    values_fill = 0
  ) %>%
  arrange(desc(n_encounters_post_enroll), desc(n_encounters_enrollment_date))

patient_class_breakdown_wide

# 3) Participant coverage: % of ALL participants with ≥1 encounter in class (by timing)
patient_class_participant <- enc_timed_class %>%
  filter(timing %in% c("enrollment_date", "post_enroll")) %>%
  group_by(timing, patient_class_clean) %>%
  summarise(
    n_participants = n_distinct(participant_id),
    .groups = "drop"
  ) %>%
  group_by(timing) %>%
  mutate(
    pct_participants_with_class = 100 * n_participants / n_distinct(enc_timed_class$participant_id)
  ) %>%
  ungroup() %>%
  arrange(timing, desc(n_participants))

patient_class_participant
```

---

## 2) Build encounter-level flags with timing + SAE-like grouping

```{r sae-encounter-flags-from-diagnoses-raw}
enc_dx_long <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, patient_class, diagnoses_raw) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  left_join(
    participants_std %>% select(participant_id, enrollment_date),
    by = "participant_id"
  ) %>%
  mutate(
    timing = case_when(
      is.na(visit_date) | is.na(enrollment_date) ~ NA_character_,
      visit_date == enrollment_date ~ "enrollment_date",
      visit_date  > enrollment_date ~ "post_enroll",
      visit_date  < enrollment_date ~ "pre_enroll"
    ),
    icd_list = extract_icd10_from_diagnoses_raw(diagnoses_raw)
  ) %>%
  unnest(icd_list, keep_empty = TRUE) %>%
  rename(icd10_raw = icd_list) %>%
  mutate(
    icd10 = clean_icd10(icd10_raw)
  ) %>%
  filter(!is.na(icd10))

enc_flags <- enc_dx_long %>%
  group_by(participant_id, csn, visit_date, enrollment_date, timing, patient_class) %>%
  summarise(
    has_suicidal_ideation = any(is_suicidal_ideation(icd10), na.rm = TRUE),
    has_suicide_attempt_or_self_harm = any(is_intentional_self_harm_or_attempt(icd10), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    sae_category = case_when(
      patient_class %in% c("Emergency", "Psych Emergency") ~ "Emergency Department (ED) visit",
      patient_class %in% c("Inpatient", "Inpatient Psych", "Observation", "Psych Observation") ~ "Inpatient hospitalization",
      TRUE ~ "Other/Unknown"
    ),
    sae_subtype = case_when(
      has_suicide_attempt_or_self_harm ~ "Suicide attempt / intentional self-harm",
      has_suicidal_ideation ~ "Suicidal ideation",
      TRUE ~ "No suicide-related ICD flag"
    )
  )
```

> I set subtype priority to **attempt/self-harm first**, then ideation, because a single encounter can contain multiple codes and you usually want “attempt” to win.

---

## 3) Visit-level tables: enrollment vs post

```{r sae-visit-level-tables}
sae_visit_table <- function(df, timing_value) {
  df %>%
    filter(timing == timing_value) %>%
    group_by(sae_category, sae_subtype) %>%
    summarise(
      n_visits = n(),
      n_participants = n_distinct(participant_id),
      .groups = "drop"
    ) %>%
    group_by(sae_category) %>%
    mutate(pct_within_category = 100 * n_visits / sum(n_visits)) %>%
    ungroup() %>%
    arrange(sae_category, desc(n_visits))
}

sae_visits_enrollment <- sae_visit_table(enc_flags, "enrollment_date")
sae_visits_post       <- sae_visit_table(enc_flags, "post_enroll")

sae_visits_enrollment
sae_visits_post
```

---

## 4) Participant-level tables: enrollment vs post

This answers “How many participants had ≥1 ED ideation / ED attempt / inpatient ideation / inpatient attempt” in each timing window.

```{r sae-participant-level-tables}
sae_participant_table <- function(df, timing_value) {
  df_t <- df %>% filter(timing == timing_value)

  df_t %>%
    group_by(participant_id) %>%
    summarise(
      any_ed_ideation = any(sae_category == "Emergency Department (ED) visit" &
                             sae_subtype == "Suicidal ideation", na.rm = TRUE),
      any_ed_attempt  = any(sae_category == "Emergency Department (ED) visit" &
                             sae_subtype == "Suicide attempt / intentional self-harm", na.rm = TRUE),
      any_ip_ideation = any(sae_category == "Inpatient hospitalization" &
                             sae_subtype == "Suicidal ideation", na.rm = TRUE),
      any_ip_attempt  = any(sae_category == "Inpatient hospitalization" &
                             sae_subtype == "Suicide attempt / intentional self-harm", na.rm = TRUE),
      .groups = "drop"
    ) %>%
    summarise(
      timing = timing_value,
      n_participants_total = n(),
      n_any_ed_ideation = sum(any_ed_ideation),
      n_any_ed_attempt  = sum(any_ed_attempt),
      n_any_ip_ideation = sum(any_ip_ideation),
      n_any_ip_attempt  = sum(any_ip_attempt)
    )
}

sae_participants_enrollment <- sae_participant_table(enc_flags, "enrollment_date")
sae_participants_post       <- sae_participant_table(enc_flags, "post_enroll")

sae_participants_enrollment
sae_participants_post
```

---

## 5) Optional: table exactly like your screenshot (ED + Inpatient with sub-checkboxes)
```{r sae-screenshot-style-table}
sae_checkbox_table <- enc_flags %>%
  filter(timing %in% c("enrollment_date", "post_enroll")) %>%
  group_by(timing, sae_category, sae_subtype) %>%
  summarise(
    n_visits = n(),
    n_participants = n_distinct(participant_id),
    .groups = "drop"
  ) %>%
  arrange(timing, sae_category, sae_subtype)

sae_checkbox_table
```
---
---

```{r}
library(dplyr)
library(lubridate)

ip_classes <- c("Inpatient", "Observation", "Inpatient Psych", "Psych Observation")
ed_classes <- c("Emergency", "Psych Emergency")

# If you only have visit_date, keep as Date.
# If you have a datetime, swap `visit_date` for that datetime variable.
enc_core <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, patient_class, encounter_type_clean = encounter_type) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE)

# 1) Build an "inpatient/obs encounter list"
ip_enc <- enc_core %>%
  filter(patient_class %in% ip_classes) %>%
  select(participant_id, csn, ip_date = visit_date)

# 2) Start from ED / Hospital encounters you want to classify
ed_or_hosp <- enc_core %>%
  filter(patient_class %in% ed_classes | encounter_type_clean == "Hospital Encounter") %>%
  mutate(ed_date = visit_date)

# 3) Admission proxy: any inpatient/obs within 0–1 days after ED date (or same CSN inpatient)
admission_flags <- ed_or_hosp %>%
  left_join(ip_enc, by = c("participant_id", "csn")) %>%
  group_by(participant_id, csn, ed_date) %>%
  summarise(
    # same CSN inpatient/obs at any time (strongest signal)
    admitted_same_csn = any(!is.na(ip_date)),

    # or inpatient/obs soon after ED (useful if CSNs differ in your export)
    admitted_within_1d = any(!is.na(ip_date) & ip_date >= ed_date & ip_date <= ed_date + days(1)),

    admitted = admitted_same_csn | admitted_within_1d,
    .groups = "drop"
  )

admission_flags
```

---
```{r}
library(dplyr)
library(lubridate)

admission_flags_timed <- admission_flags %>%
  left_join(
    participants_std %>% select(participant_id, enrollment_date),
    by = "participant_id"
  ) %>%
  mutate(
    timing = case_when(
      is.na(ed_date) | is.na(enrollment_date) ~ NA_character_,
      ed_date == enrollment_date ~ "enrollment_date",
      ed_date  > enrollment_date ~ "post_enroll",
      ed_date  < enrollment_date ~ "pre_enroll"
    )
  ) %>%
  filter(timing %in% c("enrollment_date", "post_enroll"))
```

```{r}
encounter_level_summary <- admission_flags_timed %>%
  group_by(timing) %>%
  summarise(
    n_encounters = n(),
    n_admitted_encounters = sum(admitted, na.rm = TRUE),
    pct_admitted_encounters = 100 * mean(admitted, na.rm = TRUE),
    .groups = "drop"
  )

encounter_level_summary
```

```{r}
encounter_level_counts <- admission_flags_timed %>%
  count(timing, admitted, name = "n_encounters") %>%
  mutate(admitted = ifelse(admitted, "Admitted", "Not admitted")) %>%
  arrange(timing, desc(n_encounters))

encounter_level_counts
```

```{r}
participant_level_summary <- admission_flags_timed %>%
  group_by(timing, participant_id) %>%
  summarise(
    any_encounter = TRUE,
    any_admitted_encounter = any(admitted, na.rm = TRUE),
    n_encounters = n(),
    n_admitted_encounters = sum(admitted, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(timing) %>%
  summarise(
    n_participants_with_any_encounter = n(),
    n_participants_with_any_admission = sum(any_admitted_encounter),
    pct_participants_with_any_admission = 100 * mean(any_admitted_encounter),
    mean_admitted_encounters_per_participant = mean(n_admitted_encounters),
    mean_admitted_encounters_among_admitted = mean(n_admitted_encounters[any_admitted_encounter]),
    .groups = "drop"
  )

participant_level_summary
```

```{r}
participant_admit_distribution <- admission_flags_timed %>%
  group_by(timing, participant_id) %>%
  summarise(n_admitted_encounters = sum(admitted, na.rm = TRUE), .groups = "drop") %>%
  count(timing, n_admitted_encounters, name = "n_participants") %>%
  arrange(timing, n_admitted_encounters)

participant_admit_distribution
```
---

```{r ae-selfharm-table-admission-proxy-legacy, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(readr)
library(lubridate)

# ---- REQUIRED legacy helpers must already exist ----
# clean_icd10()
# extract_icd10_from_diagnoses_raw()
# is_intentional_self_harm_or_attempt()

# Attempt code (T14.91 -> T1491 after dot removal)
is_suicide_attempt_code <- function(icd_clean) str_detect(icd_clean, "^T1491$")

# -----------------------------
# 0) Roster linkage (site + arm) + output column labels
# -----------------------------
roster_path <- "/Users/jaimiechin/Library/CloudStorage/Box-Box/WeCare (Michael Wu)/Data/cleaned/New ETL Output/dat_merged.csv"

desired_cols <- c(
  "Harlem Hospital - Control",
  "Harlem Hospital - TX",
  "Kings County Hospital - Control",
  "Kings County Hospital - TX"
)

roster_ae <- read_csv(roster_path, show_col_types = FALSE) %>%
  transmute(
    participant_id = as.character(record_id),
    site_id        = as.character(site_id),   # "H" or "K"
    treatment      = as.integer(treatment)    # 0/1
  ) %>%
  filter(!is.na(treatment), site_id %in% c("H", "K")) %>%
  mutate(
    site = if_else(site_id == "H", "Harlem Hospital", "Kings County Hospital"),
    arm  = if_else(treatment == 1, "TX", "Control"),
    col  = paste(site, arm, sep = " - ")
  ) %>%
  select(participant_id, col)

# -----------------------------
# 1) Define classes for admission proxy
# -----------------------------
ip_classes <- c("Inpatient", "Inpatient Psych", "Observation", "Psych Observation")
ed_classes <- c("Emergency", "Psych Emergency")

# "ED/Hospital encounters to evaluate for admission"
# We use ED classes or encounter_type == "Hospital Encounter" as a broad hospital-facing bucket.
enc_core <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, patient_class, encounter_type) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  mutate(
    patient_class = str_squish(patient_class),
    encounter_type = str_squish(encounter_type)
  )

ip_enc <- enc_core %>%
  filter(patient_class %in% ip_classes) %>%
  select(participant_id, csn, ip_date = visit_date)

ed_or_hosp <- enc_core %>%
  filter(patient_class %in% ed_classes | encounter_type == "Hospital Encounter") %>%
  mutate(ed_date = visit_date) %>%
  select(participant_id, csn, ed_date)

# Admission proxy: inpatient/obs encounter on same CSN OR within 1 day after ED date
admission_flags <- ed_or_hosp %>%
  left_join(ip_enc, by = c("participant_id", "csn")) %>%
  group_by(participant_id, csn, ed_date) %>%
  summarise(
    admitted_same_csn = any(!is.na(ip_date)),
    admitted_within_1d = any(!is.na(ip_date) & ip_date >= ed_date & ip_date <= ed_date + days(1)),
    admitted = admitted_same_csn | admitted_within_1d,
    .groups = "drop"
  )

# -----------------------------
# 2) Parse ICD codes from diagnoses_raw at encounter level (12m restricted)
# -----------------------------
enc_dx_long <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, patient_class, encounter_type, diagnoses_raw) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  mutate(
    patient_class = str_squish(patient_class),
    encounter_type = str_squish(encounter_type),
    icd_list = extract_icd10_from_diagnoses_raw(diagnoses_raw)
  ) %>%
  unnest(icd_list, keep_empty = FALSE) %>%
  rename(icd10_raw = icd_list) %>%
  mutate(icd10 = clean_icd10(icd10_raw)) %>%
  filter(!is.na(icd10))

# Encounter-level self-harm flags (legacy)
enc_selfharm_flags <- enc_dx_long %>%
  group_by(participant_id, csn, visit_date, patient_class, encounter_type) %>%
  summarise(
    has_attempt_code = any(is_suicide_attempt_code(icd10), na.rm = TRUE),   # T1491 only
    has_selfharm_or_attempt = any(is_intentional_self_harm_or_attempt(icd10), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    is_attempt = has_attempt_code,
    is_nssi = has_selfharm_or_attempt & !has_attempt_code,
    is_ip = patient_class %in% ip_classes,
    is_ed_or_hosp = (patient_class %in% ed_classes) | (encounter_type == "Hospital Encounter")
  ) %>%
  # attach admission proxy for ED/Hosp encounters (if not ED/Hosp, admitted stays NA -> FALSE)
  left_join(admission_flags, by = c("participant_id", "csn", "visit_date" = "ed_date")) %>%
  mutate(admitted = coalesce(admitted, FALSE))

# -----------------------------
# 3) Classify encounters into the 5 required table rows
#    Counting unit = unique encounter (participant_id + csn + visit_date)
# -----------------------------
ae_events <- bind_rows(
  # Suicide Attempts (SAE)
  enc_selfharm_flags %>%
    filter(is_attempt) %>%
    transmute(participant_id, csn, visit_date, row = "Suicide Attempts"),

  # NSSI that results in ED visit or hospitalization:
  # - any IP/Obs encounter with NSSI codes, OR
  # - ED/Hosp encounter with NSSI codes AND admission proxy TRUE
  enc_selfharm_flags %>%
    filter(is_nssi, is_ip | (is_ed_or_hosp & admitted)) %>%
    transmute(
      participant_id, csn, visit_date,
      row = "Non-suicidal self-injury that results in an ED visit or hospitalization"
    ),

  # NSSI that does NOT result in ED/hospitalization:
  # - ED/Hosp encounter with NSSI codes AND admission proxy FALSE
  enc_selfharm_flags %>%
    filter(is_nssi, is_ed_or_hosp, !admitted) %>%
    transmute(
      participant_id, csn, visit_date,
      row = "Non-suicidal self-injury that does not result in an ED visit or hospitalization"
    )
) %>%
  distinct(participant_id, csn, visit_date, row)

# Add totals per encounter
ae_events_with_totals <- bind_rows(
  ae_events,
  ae_events %>%
    filter(row %in% c(
      "Suicide Attempts",
      "Non-suicidal self-injury that results in an ED visit or hospitalization"
    )) %>%
    transmute(participant_id, csn, visit_date, row = "Total SAEs") %>%
    distinct(),
  ae_events %>%
    filter(row %in% c(
      "Suicide Attempts",
      "Non-suicidal self-injury that results in an ED visit or hospitalization",
      "Non-suicidal self-injury that does not result in an ED visit or hospitalization"
    )) %>%
    transmute(participant_id, csn, visit_date, row = "Total Self-harm AEs") %>%
    distinct()
)

# -----------------------------
# 4) Assemble the DSMB-style table (force all rows + columns even if 0)
# -----------------------------
row_order <- c(
  "Total SAEs",
  "Suicide Attempts",
  "Non-suicidal self-injury that results in an ED visit or hospitalization",
  "Total Self-harm AEs",
  "Non-suicidal self-injury that does not result in an ED visit or hospitalization"
)

counts_long <- ae_events_with_totals %>%
  inner_join(roster_ae, by = "participant_id") %>%
  count(row, col, name = "n") %>%
  tidyr::complete(
    row = row_order,
    col = desired_cols,
    fill = list(n = 0L)
  )

cumulative <- ae_events_with_totals %>%
  count(row, name = "Cumulative") %>%
  tidyr::complete(
    row = row_order,
    fill = list(Cumulative = 0L)
  )

ae_table_selfharm_admit_proxy <- counts_long %>%
  pivot_wider(names_from = col, values_from = n, values_fill = 0L) %>%
  left_join(cumulative, by = "row") %>%
  mutate(row = factor(row, levels = row_order)) %>%
  arrange(row) %>%
  rename(`# of AEs` = row) %>%
  select(
    `# of AEs`,
    Cumulative,
    `Harlem Hospital - Control`,
    `Harlem Hospital - TX`,
    `Kings County Hospital - Control`,
    `Kings County Hospital - TX`
  )

ae_table_selfharm_admit_proxy
```

```{r adam-selfharm-table, message=FALSE, warning=FALSE}
is_suicidal_thoughts <- function(icd) icd == "R45851"
is_suicide_attempt   <- function(icd) icd == "T1491"

is_intentional_self_harm_mechanism <- function(icd) {
  starts_T36_T65 <- str_detect(icd, "^T(3[6-9]|[4-5][0-9]|6[0-5])")
  intent_digit_5_or_6_is_2 <- (str_sub(icd, 5, 5) == "2") | (str_sub(icd, 6, 6) == "2")
  poisoning_flag <- starts_T36_T65 & intent_digit_5_or_6_is_2

  t71_flag <- str_detect(icd, "^T71") & ((str_sub(icd, 6, 6) == "2") | (str_sub(icd, 5, 5) == "2"))
  x71_x82_flag <- str_detect(icd, "^(X71|X72|X73|X74|X75|X76|X77|X78|X79|X80|X81|X82)")
  x83_0_flag <- str_detect(icd, "^X830")
  x83_other_flag <- str_detect(icd, "^(X831|X832|X838)")

  poisoning_flag | t71_flag | x71_x82_flag | x83_0_flag | x83_other_flag
}

roster_key_adam <- roster_key %>%
  filter(site_id %in% c("H", "K")) %>%
  mutate(
    arm = case_when(
      treatment == 1 ~ "TX",
      treatment == 0 ~ "Control",
      TRUE ~ NA_character_
    ),
    group = paste(site, arm, sep = " - ")
  ) %>%
  select(participant_id, group, site, arm, treatment, site_id)

enc_dx_long <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, diagnoses_raw) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  left_join(participants_std %>% select(participant_id, enrollment_date), by = "participant_id") %>%
  mutate(icd_list = extract_icd10_from_diagnoses_raw(diagnoses_raw)) %>%
  unnest(icd_list, keep_empty = FALSE) %>%
  rename(icd10_raw = icd_list) %>%
  mutate(icd10 = clean_icd10(icd10_raw)) %>%
  filter(!is.na(icd10))

enc_flags <- enc_dx_long %>%
  group_by(participant_id, csn, visit_date, enrollment_date) %>%
  summarise(
    has_attempt  = any(is_suicide_attempt(icd10), na.rm = TRUE),
    has_ideation = any(is_suicidal_thoughts(icd10), na.rm = TRUE),
    has_nssi_mech = any(is_intentional_self_harm_mechanism(icd10), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    in_all_events_window = !is.na(visit_date) & !is.na(enrollment_date) & visit_date >= enrollment_date,
    in_post_enroll_window = !is.na(visit_date) & !is.na(enrollment_date) & visit_date > enrollment_date,
    event_type = case_when(
      has_attempt ~ "Suicide attempts (T14.91)",
      !has_attempt & has_ideation ~ "Suicidal thoughts (R45.851)",
      !has_attempt & !has_ideation & has_nssi_mech ~ "Non-suicidal self-injury (intentional self-harm mechanism codes)",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(event_type)) %>%
  left_join(roster_key_adam, by = "participant_id") %>%
  filter(!is.na(treatment))

events_all <- enc_flags %>%
  filter(in_all_events_window) %>%
  count(group, event_type, name = "n_events_all")

events_post <- enc_flags %>%
  filter(in_post_enroll_window) %>%
  count(group, event_type, name = "n_events_post")

adam_table_long <- full_join(events_all, events_post, by = c("group", "event_type")) %>%
  mutate(
    n_events_all  = coalesce(n_events_all, 0L),
    n_events_post = coalesce(n_events_post, 0L)
  )

group_order <- c(
  "Harlem - Control", "Harlem - TX",
  "Kings - Control",  "Kings - TX"
)

adam_table <- adam_table_long %>%
  mutate(group = factor(group, levels = group_order)) %>%
  arrange(event_type, group) %>%
  pivot_wider(
    names_from = group,
    values_from = c(n_events_all, n_events_post),
    values_fill = 0
  )

adam_table
```

```{r adam-table-final-dropin, message=FALSE, warning=FALSE}
roster_key_adam2 <- roster_key %>%
  filter(site_id %in% c("H", "K")) %>%
  mutate(
    arm = case_when(
      treatment == 1 ~ "TX",
      treatment == 0 ~ "Control",
      TRUE ~ NA_character_
    ),
    group = paste(site, arm, sep = " - ")
  ) %>%
  select(participant_id, site, arm, group)

is_suicidal_thoughts <- function(icd) icd == "R45851"
is_suicide_attempt   <- function(icd) icd == "T1491"

is_intentional_self_harm_mechanism <- function(icd) {
  starts_T36_T65 <- str_detect(icd, "^T(3[6-9]|[4-5][0-9]|6[0-5])")
  intent_digit_5_or_6_is_2 <- (str_sub(icd, 5, 5) == "2") | (str_sub(icd, 6, 6) == "2")
  poisoning_flag <- starts_T36_T65 & intent_digit_5_or_6_is_2
  t71_flag <- str_detect(icd, "^T71") & ((str_sub(icd, 6, 6) == "2") | (str_sub(icd, 5, 5) == "2"))
  x71_x82_flag <- str_detect(icd, "^(X71|X72|X73|X74|X75|X76|X77|X78|X79|X80|X81|X82)")
  x83_0_flag <- str_detect(icd, "^X830")
  x83_other_flag <- str_detect(icd, "^(X831|X832|X838)")
  poisoning_flag | t71_flag | x71_x82_flag | x83_0_flag | x83_other_flag
}

enc_dx_long <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, diagnoses_raw) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  left_join(participants_std %>% select(participant_id, enrollment_date), by = "participant_id") %>%
  mutate(icd_list = extract_icd10_from_diagnoses_raw(diagnoses_raw)) %>%
  unnest(icd_list, keep_empty = FALSE) %>%
  rename(icd10_raw = icd_list) %>%
  mutate(icd10 = clean_icd10(icd10_raw)) %>%
  filter(!is.na(icd10))

enc_flags <- enc_dx_long %>%
  group_by(participant_id, csn, visit_date, enrollment_date) %>%
  summarise(
    has_attempt  = any(is_suicide_attempt(icd10), na.rm = TRUE),
    has_ideation = any(is_suicidal_thoughts(icd10), na.rm = TRUE),
    has_nssi_mech = any(is_intentional_self_harm_mechanism(icd10), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    in_all_events_window  = !is.na(visit_date) & !is.na(enrollment_date) & visit_date >= enrollment_date,
    in_post_enroll_window = !is.na(visit_date) & !is.na(enrollment_date) & visit_date > enrollment_date,
    event_type = case_when(
      has_attempt ~ "Suicide attempts (T14.91)",
      !has_attempt & has_ideation ~ "Suicidal thoughts (R45.851)",
      !has_attempt & !has_ideation & has_nssi_mech ~ "Non-suicidal self-injury (intentional self-harm mechanism codes)",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(event_type)) %>%
  left_join(roster_key_adam2, by = "participant_id") %>%
  filter(!is.na(group))

enc_flags_tot <- bind_rows(
  enc_flags,
  enc_flags %>% mutate(group = paste("Total -", arm)),
  enc_flags %>% mutate(group = paste(site, "- Total")),
  enc_flags %>% mutate(group = "Total - Total")
)

event_levels <- c(
  "Suicidal thoughts (R45.851)",
  "Suicide attempts (T14.91)",
  "Non-suicidal self-injury (intentional self-harm mechanism codes)"
)

group_order <- c(
  "Harlem - Control", "Harlem - TX",
  "Kings - Control",  "Kings - TX",
  "Total - Control",  "Total - TX",
  "Harlem - Total",   "Kings - Total",
  "Total - Total"
)

adam_long <- enc_flags_tot %>%
  group_by(group, event_type) %>%
  summarise(
    n_events_all  = sum(in_all_events_window, na.rm = TRUE),
    n_events_post = sum(in_post_enroll_window, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    event_type = factor(event_type, levels = event_levels),
    group = factor(group, levels = group_order)
  ) %>%
  complete(
    event_type,
    group,
    fill = list(n_events_all = 0L, n_events_post = 0L)
  ) %>%
  arrange(event_type, group)

adam_table <- adam_long %>%
  pivot_wider(
    names_from = group,
    values_from = c(n_events_all, n_events_post),
    values_fill = 0L
  )

adam_table
```

```{r adam-two-tables-all-vs-post}
# Assumes your wide output is named `adam_table`
# (If it's named differently, replace adam_table below.)

adam_all <- adam_table %>%
  transmute(
    event_type,
    `Harlem – Control` = `n_events_all_Harlem - Control`,
    `Harlem – TX`      = `n_events_all_Harlem - TX`,
    `Kings – Control`  = `n_events_all_Kings - Control`,
    `Kings – TX`       = `n_events_all_Kings - TX`,
    `Cumulative`       = `Harlem – Control` + `Harlem – TX` + `Kings – Control` + `Kings – TX`
  )

adam_post <- adam_table %>%
  transmute(
    event_type,
    `Harlem – Control` = `n_events_post_Harlem - Control`,
    `Harlem – TX`      = `n_events_post_Harlem - TX`,
    `Kings – Control`  = `n_events_post_Kings - Control`,
    `Kings – TX`       = `n_events_post_Kings - TX`,
    `Cumulative`       = `Harlem – Control` + `Harlem – TX` + `Kings – Control` + `Kings – TX`
  )

adam_all
adam_post
```

```{r selfharm-reports-linelist-4-6, message=FALSE, warning=FALSE}
roster_key_linelist <- roster_key %>%
  mutate(
    tx_group_linelist = case_when(
      treatment == 1 ~ "Treatment",
      treatment == 0 ~ "Control",
      TRUE ~ "Unknown"
    )
  ) %>%
  select(participant_id, tx_group_linelist, site)

ip_classes <- c("Inpatient", "Observation", "Inpatient Psych", "Psych Observation")
ed_classes <- c("Emergency", "Psych Emergency")

enc_core_linelist <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, patient_class, encounter_type) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  mutate(
    patient_class = str_squish(patient_class),
    encounter_type = str_squish(encounter_type)
  )

ip_enc <- enc_core_linelist %>%
  filter(patient_class %in% ip_classes) %>%
  select(participant_id, csn, ip_date = visit_date)

ed_or_hosp <- enc_core_linelist %>%
  filter(patient_class %in% ed_classes | encounter_type == "Hospital Encounter") %>%
  transmute(participant_id, csn, ed_date = visit_date)

admission_flags <- ed_or_hosp %>%
  left_join(ip_enc, by = c("participant_id", "csn")) %>%
  group_by(participant_id, csn, ed_date) %>%
  summarise(
    admitted_same_csn = any(!is.na(ip_date)),
    admitted_within_1d = any(!is.na(ip_date) & ip_date >= ed_date & ip_date <= ed_date + days(1)),
    admitted = admitted_same_csn | admitted_within_1d,
    .groups = "drop"
  )

enc_dx_long <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, patient_class, encounter_type, diagnoses_raw, procedures_raw) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  left_join(participants_std %>% select(participant_id, enrollment_date), by = "participant_id") %>%
  mutate(icd_list = extract_icd10_from_diagnoses_raw(diagnoses_raw)) %>%
  unnest(icd_list, keep_empty = FALSE) %>%
  rename(icd10_raw = icd_list) %>%
  mutate(
    icd10 = clean_icd10(icd10_raw),
    patient_class = str_squish(patient_class),
    encounter_type = str_squish(encounter_type)
  ) %>%
  filter(!is.na(icd10))

is_suicidal_thoughts <- function(icd_clean) icd_clean == "R45851"
is_suicide_attempt_code <- function(icd_clean) icd_clean == "T1491"

enc_flags <- enc_dx_long %>%
  group_by(participant_id, csn, visit_date, enrollment_date, patient_class, encounter_type, procedures_raw) %>%
  summarise(
    has_attempt  = any(is_suicide_attempt_code(icd10), na.rm = TRUE),
    has_ideation = any(is_suicidal_thoughts(icd10), na.rm = TRUE),
    has_nssi_mech = any(is_intentional_self_harm_or_attempt(icd10), na.rm = TRUE),
    attempt_codes = paste(sort(unique(icd10[is_suicide_attempt_code(icd10)])), collapse = ", "),
    ideation_codes = paste(sort(unique(icd10[is_suicidal_thoughts(icd10)])), collapse = ", "),
    nssi_codes = paste(sort(unique(icd10[is_intentional_self_harm_or_attempt(icd10) & !is_suicide_attempt_code(icd10)])), collapse = ", "),
    .groups = "drop"
  ) %>%
  mutate(
    is_enrollment_day = !is.na(enrollment_date) & !is.na(visit_date) & visit_date == enrollment_date,
    weeks_in_study = if_else(
      !is.na(enrollment_date) & !is.na(visit_date),
      as.integer(floor(as.numeric(difftime(visit_date, enrollment_date, units = "days")) / 7)),
      NA_integer_
    )
  ) %>%
  left_join(admission_flags, by = c("participant_id", "csn", "visit_date" = "ed_date")) %>%
  mutate(admitted = coalesce(admitted, FALSE)) %>%
  mutate(
    event_type = case_when(
      has_attempt ~ "Suicide attempt",
      !has_attempt & has_nssi_mech ~ "NSSI / intentional self-harm (mechanism codes)",
      !has_attempt & !has_nssi_mech & has_ideation ~ "Suicidal thoughts",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(event_type %in% c("Suicide attempt", "NSSI / intentional self-harm (mechanism codes)")) %>%
  mutate(
    is_ip = patient_class %in% ip_classes,
    is_ed_or_hosp = (patient_class %in% ed_classes) | (encounter_type == "Hospital Encounter"),
    event_class = case_when(
      event_type == "Suicide attempt" ~ "SAE",
      event_type == "NSSI / intentional self-harm (mechanism codes)" & (is_ip | (is_ed_or_hosp & admitted)) ~ "SAE",
      event_type == "NSSI / intentional self-harm (mechanism codes)" ~ "AE",
      TRUE ~ NA_character_
    ),
    date_of_event = paste0(as.character(visit_date), if_else(is_enrollment_day, " (enrollment)", ""))
  )

has_procedure_note <- function(x) !is.na(x) & str_trim(x) != ""

enc_flags <- enc_flags %>%
  mutate(
    treatment_received_for_attempt = case_when(
      event_type == "Suicide attempt" ~ has_procedure_note(procedures_raw),
      TRUE ~ NA
    ),
    procedures_note = case_when(
      event_type == "Suicide attempt" & has_procedure_note(procedures_raw) ~ str_squish(procedures_raw),
      TRUE ~ NA_character_
    )
  )

attempt_max_date <- enc_flags %>%
  filter(event_type == "Suicide attempt") %>%
  group_by(participant_id) %>%
  summarise(max_attempt_date = max(visit_date, na.rm = TRUE), .groups = "drop")

enc_flags <- enc_flags %>%
  left_join(attempt_max_date, by = "participant_id") %>%
  mutate(
    most_recent_attempt_if_no_treatment = case_when(
      event_type != "Suicide attempt" ~ NA,
      treatment_received_for_attempt %in% TRUE ~ NA,
      treatment_received_for_attempt %in% FALSE ~ (visit_date == max_attempt_date),
      TRUE ~ NA
    )
  )

events_for_report <- enc_flags %>%
  left_join(roster_key_linelist, by = "participant_id") %>%
  mutate(
    tx_group_linelist = coalesce(tx_group_linelist, "Unknown"),
    trigger_code = case_when(
      event_type == "Suicide attempt" ~ "T14.91 (T1491)",
      event_type == "NSSI / intentional self-harm (mechanism codes)" ~ "Intentional self-harm mechanism codes (T36–T65 intent=2; T71 intent=2; X71–X83.*)",
      TRUE ~ NA_character_
    ),
    trigger_meaning = case_when(
      event_type == "Suicide attempt" ~ "Suicide attempt ICD-10 code",
      event_type == "NSSI / intentional self-harm (mechanism codes)" ~ "Mechanism-based intentional self-harm ICD-10 codes (excludes suicidal ideation and excludes T14.91)",
      TRUE ~ NA_character_
    )
  ) %>%
  arrange(event_class, visit_date, participant_id, csn) %>%
  group_by(event_class) %>%
  mutate(
    event_number = row_number(),
    `SAE#/AE#` = paste0(
      event_class, "-", str_pad(event_number, width = 3, pad = "0"),
      " | ", trigger_code, " | ", trigger_meaning
    )
  ) %>%
  ungroup() %>%
  select(
    `SAE#/AE#`,
    `TX Group` = tx_group_linelist,
    `Subject ID` = participant_id,
    `Date of Event` = date_of_event,
    `Week in Study` = weeks_in_study,
    `Was treatment received for attempt?` = treatment_received_for_attempt,
    `Procedures note (if any)` = procedures_note,
    `If no treatment, was this the most recent attempt?` = most_recent_attempt_if_no_treatment
  )

events_for_report
```

```{r qc-ideation-attempt-participants-vs-events, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)

# Uses your existing encounter-level ICD parsing pipeline (12m restricted)
# enc_dx_long should have: participant_id, csn, visit_date, enrollment_date, icd10 (dot-removed)
# If not, rebuild quickly from encounters_std_12m:
enc_dx_long <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, diagnoses_raw) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  left_join(participants_std %>% select(participant_id, enrollment_date), by = "participant_id") %>%
  mutate(icd_list = extract_icd10_from_diagnoses_raw(diagnoses_raw)) %>%
  unnest(icd_list, keep_empty = FALSE) %>%
  rename(icd10_raw = icd_list) %>%
  mutate(icd10 = clean_icd10(icd10_raw)) %>%
  filter(!is.na(icd10))

# Definitions Adam is referencing
is_ideation <- function(icd) icd == "R45851"  # R45.851
is_attempt  <- function(icd) icd == "T1491"   # T14.91

enc_event_flags <- enc_dx_long %>%
  group_by(participant_id, csn, visit_date, enrollment_date) %>%
  summarise(
    has_ideation = any(is_ideation(icd10), na.rm = TRUE),
    has_attempt  = any(is_attempt(icd10), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    timing = case_when(
      is.na(visit_date) | is.na(enrollment_date) ~ NA_character_,
      visit_date == enrollment_date ~ "enrollment_day",
      visit_date >  enrollment_date ~ "post_enrollment",
      TRUE ~ "pre_enrollment"
    ),
    in_all = !is.na(timing) & timing %in% c("enrollment_day", "post_enrollment"),
    in_post = !is.na(timing) & timing == "post_enrollment"
  )

qc_summary <- bind_rows(
  enc_event_flags %>%
    filter(in_all) %>%
    summarise(
      window = "All (>= enrollment)",
      n_events_ideation = sum(has_ideation),
      n_participants_ideation = n_distinct(participant_id[has_ideation]),
      n_events_attempt = sum(has_attempt),
      n_participants_attempt = n_distinct(participant_id[has_attempt]),
      n_events_either = sum(has_ideation | has_attempt),
      n_participants_either = n_distinct(participant_id[has_ideation | has_attempt])
    ),
  enc_event_flags %>%
    filter(in_post) %>%
    summarise(
      window = "Post-enrollment (> enrollment)",
      n_events_ideation = sum(has_ideation),
      n_participants_ideation = n_distinct(participant_id[has_ideation]),
      n_events_attempt = sum(has_attempt),
      n_participants_attempt = n_distinct(participant_id[has_attempt]),
      n_events_either = sum(has_ideation | has_attempt),
      n_participants_either = n_distinct(participant_id[has_ideation | has_attempt])
    )
)

qc_summary
```

```{r qc-post-enroll-selfharm-code-frequency, message=FALSE, warning=FALSE}
# Mechanism-based self-harm family (dot-removed)
is_mechanism_selfharm <- function(icd) {
  starts_T36_T65 <- str_detect(icd, "^T(3[6-9]|[4-5][0-9]|6[0-5])")
  intent_digit_5_or_6_is_2 <- (str_sub(icd, 5, 5) == "2") | (str_sub(icd, 6, 6) == "2")
  poisoning_flag <- starts_T36_T65 & intent_digit_5_or_6_is_2
  t71_flag <- str_detect(icd, "^T71") & ((str_sub(icd, 6, 6) == "2") | (str_sub(icd, 5, 5) == "2"))
  x71_x82_flag <- str_detect(icd, "^(X71|X72|X73|X74|X75|X76|X77|X78|X79|X80|X81|X82)")
  x83_flag <- str_detect(icd, "^(X830|X831|X832|X838)")
  poisoning_flag | t71_flag | x71_x82_flag | x83_flag
}

post_codes <- enc_dx_long %>%
  filter(!is.na(visit_date), !is.na(enrollment_date), visit_date > enrollment_date) %>%
  filter(is_ideation(icd10) | is_attempt(icd10) | is_mechanism_selfharm(icd10)) %>%
  count(icd10, sort = TRUE)

post_codes
```

```{r suicidality-adjacent-mh-mutually-exclusive-events-and-participants, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)

# ---- Assumes these exist from earlier in your Rmd ----
# clean_icd10()
# extract_icd10_from_diagnoses_raw()
# encounters_std_12m
# participants_std (participant_id, enrollment_date)

# -----------------------------
# 1) Setting classification (mutually exclusive)
# -----------------------------
ed_classes <- c("Emergency", "Psych Emergency")
ip_classes <- c("Inpatient", "Inpatient Psych", "Observation", "Psych Observation")

classify_setting <- function(patient_class) {
  pc <- str_squish(as.character(patient_class))
  dplyr::case_when(
    pc %in% ed_classes ~ "Emergency Department (ED) visit",
    pc %in% ip_classes ~ "Inpatient hospitalization",
    TRUE ~ "Other/Unknown"
  )
}

setting_order <- c(
  "Emergency Department (ED) visit",
  "Inpatient hospitalization",
  "Other/Unknown"
)

# -----------------------------
# 2) ICD definitions (dot removed)
# -----------------------------
is_SA <- function(icd) icd == "T1491"   # T14.91
is_SI <- function(icd) icd == "R45851"  # R45.851

is_selfharm_mechanism <- function(icd) {
  starts_T36_T65 <- str_detect(icd, "^T(3[6-9]|[4-5][0-9]|6[0-5])")
  intent_digit_5_or_6_is_2 <- (str_sub(icd, 5, 5) == "2") | (str_sub(icd, 6, 6) == "2")
  poisoning_flag <- starts_T36_T65 & intent_digit_5_or_6_is_2

  t71_flag <- str_detect(icd, "^T71") & ((str_sub(icd, 6, 6) == "2") | (str_sub(icd, 5, 5) == "2"))

  x71_x82_flag <- str_detect(icd, "^(X71|X72|X73|X74|X75|X76|X77|X78|X79|X80|X81|X82)")
  x83_flag <- str_detect(icd, "^(X830|X831|X832|X838)")

  poisoning_flag | t71_flag | x71_x82_flag | x83_flag
}

# Adjacent MH buckets (dot removed)
is_depression <- function(icd) str_detect(icd, "^F3(2|3)")  # F32–F33
is_anxiety    <- function(icd) str_detect(icd, "^F4(0|1)")  # F40–F41
is_adjustment <- function(icd) str_detect(icd, "^F432")     # F43.2*
is_ptsd       <- function(icd) str_detect(icd, "^F431")     # F43.1*
is_adhd       <- function(icd) str_detect(icd, "^F90")      # F90*
is_substance  <- function(icd) str_detect(icd, "^F1[0-9]")  # F10–F19 (optional)

# Mutually exclusive category priority order (edit if desired)
category_order <- c(
  "Suicide attempt (T14.91)",
  "Suicidal ideation (R45.851)",
  "Intentional self-harm mechanism codes (X71–X83.*, T36–T65 intent=2, T71 intent=2)",
  "Depression (F32–F33)",
  "Anxiety (F40–F41)",
  "Adjustment disorder (F43.2)",
  "PTSD/trauma-related (F43.1)",
  "ADHD (F90)",
  "Substance use disorders (F10–F19)"
)

# -----------------------------
# 3) Build encounter-level ICD table (one row per ICD per encounter)
# -----------------------------
enc_dx_long <- encounters_std_12m %>%
  select(participant_id, csn, visit_date, patient_class, diagnoses_raw) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  left_join(participants_std %>% select(participant_id, enrollment_date), by = "participant_id") %>%
  mutate(
    setting = classify_setting(patient_class),
    timing = case_when(
      is.na(visit_date) | is.na(enrollment_date) ~ NA_character_,
      visit_date == enrollment_date ~ "enrollment_day",
      visit_date >  enrollment_date ~ "post_enrollment",
      visit_date <  enrollment_date ~ "pre_enrollment"
    ),
    icd_list = extract_icd10_from_diagnoses_raw(diagnoses_raw)
  ) %>%
  unnest(icd_list, keep_empty = FALSE) %>%
  rename(icd10_raw = icd_list) %>%
  mutate(icd10 = clean_icd10(icd10_raw)) %>%
  filter(!is.na(icd10))

# -----------------------------
# 4) Collapse to encounter-level flags + mutually exclusive category
# -----------------------------
enc_mh_flags <- enc_dx_long %>%
  group_by(participant_id, csn, visit_date, setting, timing) %>%
  summarise(
    has_SA = any(is_SA(icd10), na.rm = TRUE),
    has_SI = any(is_SI(icd10), na.rm = TRUE),
    has_selfharm_mech = any(is_selfharm_mechanism(icd10), na.rm = TRUE),

    has_dep = any(is_depression(icd10), na.rm = TRUE),
    has_anx = any(is_anxiety(icd10), na.rm = TRUE),
    has_adj = any(is_adjustment(icd10), na.rm = TRUE),
    has_ptsd = any(is_ptsd(icd10), na.rm = TRUE),
    has_adhd = any(is_adhd(icd10), na.rm = TRUE),
    has_subst = any(is_substance(icd10), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    mh_category = case_when(
      has_SA ~ "Suicide attempt (T14.91)",
      !has_SA & has_SI ~ "Suicidal ideation (R45.851)",
      !has_SA & !has_SI & has_selfharm_mech ~ "Intentional self-harm mechanism codes (X71–X83.*, T36–T65 intent=2, T71 intent=2)",
      !has_SA & !has_SI & !has_selfharm_mech & has_dep ~ "Depression (F32–F33)",
      !has_SA & !has_SI & !has_selfharm_mech & !has_dep & has_anx ~ "Anxiety (F40–F41)",
      !has_SA & !has_SI & !has_selfharm_mech & !has_dep & !has_anx & has_adj ~ "Adjustment disorder (F43.2)",
      !has_SA & !has_SI & !has_selfharm_mech & !has_dep & !has_anx & !has_adj & has_ptsd ~ "PTSD/trauma-related (F43.1)",
      !has_SA & !has_SI & !has_selfharm_mech & !has_dep & !has_anx & !has_adj & !has_ptsd & has_adhd ~ "ADHD (F90)",
      !has_SA & !has_SI & !has_selfharm_mech & !has_dep & !has_anx & !has_adj & !has_ptsd & !has_adhd & has_subst ~ "Substance use disorders (F10–F19)",
      TRUE ~ NA_character_
    ),
    mh_category = factor(mh_category, levels = category_order),
    setting = factor(setting, levels = setting_order)
  ) %>%
  filter(!is.na(mh_category))

# Helper to build event-count table
make_event_table <- function(df, title_label) {
  df %>%
    count(setting, mh_category, name = "n_events") %>%
    tidyr::complete(setting, mh_category, fill = list(n_events = 0L)) %>%
    pivot_wider(names_from = setting, values_from = n_events, values_fill = 0L) %>%
    mutate(`Total (events)` = rowSums(across(all_of(setting_order)))) %>%
    arrange(mh_category) %>%
    mutate(Window = title_label) %>%
    select(Window, `Category (mutually exclusive)` = mh_category, all_of(setting_order), `Total (events)`)
}

# Helper to build participant-count table
make_participant_table <- function(df, title_label) {
  df %>%
    group_by(setting, mh_category) %>%
    summarise(n_participants = n_distinct(participant_id), .groups = "drop") %>%
    tidyr::complete(setting, mh_category, fill = list(n_participants = 0L)) %>%
    pivot_wider(names_from = setting, values_from = n_participants, values_fill = 0L) %>%
    mutate(`Total (participants)` = rowSums(across(all_of(setting_order)))) %>%
    arrange(mh_category) %>%
    mutate(Window = title_label) %>%
    select(Window, `Category (mutually exclusive)` = mh_category, all_of(setting_order), `Total (participants)`)
}

# Define the two windows:
df_all  <- enc_mh_flags %>% filter(timing %in% c("enrollment_day", "post_enrollment"))
df_post <- enc_mh_flags %>% filter(timing == "post_enrollment")

# 1) All events — event counts
tbl_all_events <- make_event_table(df_all, "All (>= enrollment)")

# 2) All events — participant counts
tbl_all_participants <- make_participant_table(df_all, "All (>= enrollment)")

# 3) Post-enrollment — event counts
tbl_post_events <- make_event_table(df_post, "Post-enrollment (> enrollment)")

# 4) Post-enrollment — participant counts
tbl_post_participants <- make_participant_table(df_post, "Post-enrollment (> enrollment)")

tbl_all_events
tbl_all_participants
tbl_post_events
tbl_post_participants
```

```{r mh-overlap-matrix-all-vs-post, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)

# Assumes you already built enc_dx_long with:
# participant_id, csn, visit_date, enrollment_date, icd10 (dot removed)
# If not, use the enc_dx_long creation from earlier sections.

# ---- Define categories you want in the matrix ----
# You can add/remove categories here.
mh_cats <- tibble::tribble(
  ~cat, ~fn,
  "Suicidal ideation (R45.851)", function(x) x == "R45851",
  "Suicide attempt (T14.91)",   function(x) x == "T1491",
  "Self-harm mechanism codes (X/T intent)", function(x) {
    starts_T36_T65 <- str_detect(x, "^T(3[6-9]|[4-5][0-9]|6[0-5])")
    intent_digit_5_or_6_is_2 <- (str_sub(x, 5, 5) == "2") | (str_sub(x, 6, 6) == "2")
    poisoning_flag <- starts_T36_T65 & intent_digit_5_or_6_is_2
    t71_flag <- str_detect(x, "^T71") & ((str_sub(x, 6, 6) == "2") | (str_sub(x, 5, 5) == "2"))
    x71_x82_flag <- str_detect(x, "^(X71|X72|X73|X74|X75|X76|X77|X78|X79|X80|X81|X82)")
    x83_flag <- str_detect(x, "^(X830|X831|X832|X838)")
    poisoning_flag | t71_flag | x71_x82_flag | x83_flag
  },
  "Depression (F32–F33)",       function(x) str_detect(x, "^F3(2|3)"),
  "Anxiety (F40–F41)",          function(x) str_detect(x, "^F4(0|1)"),
  "Adjustment disorder (F43.2)",function(x) str_detect(x, "^F432"),
  "PTSD/trauma-related (F43.1)",function(x) str_detect(x, "^F431"),
  "ADHD (F90)",                 function(x) str_detect(x, "^F90"),
  "Substance use (F10–F19)",    function(x) str_detect(x, "^F1[0-9]")
)

cat_order <- mh_cats$cat

# ---- Helper: build participant x category flags for a given timing window ----
make_participant_flags <- function(dx_long, window = c("all_ge_enroll", "post_only")) {
  window <- match.arg(window)

  dx2 <- dx_long %>%
    filter(!is.na(visit_date), !is.na(enrollment_date)) %>%
    mutate(
      timing = case_when(
        visit_date == enrollment_date ~ "enrollment_day",
        visit_date >  enrollment_date ~ "post_enrollment",
        visit_date <  enrollment_date ~ "pre_enrollment"
      )
    )

  dx2 <- if (window == "all_ge_enroll") {
    dx2 %>% filter(timing %in% c("enrollment_day", "post_enrollment"))
  } else {
    dx2 %>% filter(timing == "post_enrollment")
  }

  # Compute any() by participant for each category
  flags_list <- lapply(seq_len(nrow(mh_cats)), function(i) {
    nm <- mh_cats$cat[i]
    fn <- mh_cats$fn[[i]]
    dx2 %>%
      group_by(participant_id) %>%
      summarise(val = any(fn(icd10), na.rm = TRUE), .groups = "drop") %>%
      rename(!!nm := val)
  })

  Reduce(function(x, y) full_join(x, y, by = "participant_id"), flags_list) %>%
    mutate(across(all_of(cat_order), ~coalesce(.x, FALSE)))
}

# ---- Helper: overlap matrices (counts + row-conditional %) ----
overlap_count_matrix <- function(flags_df) {
  mat <- as.matrix(flags_df[, cat_order, drop = FALSE])
  storage.mode(mat) <- "numeric"
  # crossproduct gives counts of co-occurrence (TRUE treated as 1)
  out <- t(mat) %*% mat
  out <- as.data.frame(out)
  out <- tibble::rownames_to_column(out, "Row category")
  out
}

overlap_row_pct_matrix <- function(count_df) {
  # convert count_df (wide) to row % (conditional on row diagonal)
  num <- as.matrix(count_df[, -1, drop = FALSE])
  diag_n <- diag(num)
  pct <- sweep(num, 1, diag_n, FUN = function(x, d) ifelse(d == 0, NA_real_, 100 * x / d))
  pct_df <- as.data.frame(round(pct, 1))
  pct_df <- tibble::add_column(pct_df, `Row category` = count_df$`Row category`, .before = 1)
  pct_df
}

# ---- Build ALL (>= enrollment) matrices ----
flags_all <- make_participant_flags(enc_dx_long, window = "all_ge_enroll")
overlap_all_counts <- overlap_count_matrix(flags_all)
overlap_all_rowpct  <- overlap_row_pct_matrix(overlap_all_counts)

# ---- Build POST-only matrices ----
flags_post <- make_participant_flags(enc_dx_long, window = "post_only")
overlap_post_counts <- overlap_count_matrix(flags_post)
overlap_post_rowpct  <- overlap_row_pct_matrix(overlap_post_counts)

# Outputs
overlap_all_counts
overlap_all_rowpct

overlap_post_counts
overlap_post_rowpct
```

```{r icd10-descriptives-overall, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)

# Build diagnoses_long from 12m encounters (if you don't already have it)
diagnoses_long_12m <- encounters_std_12m %>%
  select(participant_id, visit_date, csn, diagnoses_raw) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  mutate(
    codes = purrr::map(diagnoses_raw, extract_icd10_parentheses)  # if you used this version
    # OR: codes = extract_icd10_from_diagnoses_raw(diagnoses_raw) %>% ... if you're using legacy list extractor
  ) %>%
  tidyr::unnest(codes) %>%
  transmute(
    participant_id,
    visit_date,
    diagnosis_code = clean_icd10(codes)   # dot removed standardized
  ) %>%
  filter(!is.na(diagnosis_code))

icd10_overall <- diagnoses_long_12m %>%
  group_by(diagnosis_code) %>%
  summarise(
    n_events = n(),                            # code occurrences across encounters
    n_participants = n_distinct(participant_id),
    .groups = "drop"
  ) %>%
  arrange(desc(n_participants), desc(n_events))

# Top 30 by participant prevalence
icd10_overall
```

```{r icd10-coverage-summary, message=FALSE, warning=FALSE}
icd10_coverage <- diagnoses_long_12m %>%
  group_by(participant_id) %>%
  summarise(n_unique_codes = n_distinct(diagnosis_code), .groups = "drop")

tibble(
  n_unique_icd10_codes_total = n_distinct(diagnoses_long_12m$diagnosis_code),
  median_unique_codes_per_participant = median(icd10_coverage$n_unique_codes, na.rm = TRUE),
  p25_unique_codes_per_participant = quantile(icd10_coverage$n_unique_codes, 0.25, na.rm = TRUE),
  p75_unique_codes_per_participant = quantile(icd10_coverage$n_unique_codes, 0.75, na.rm = TRUE)
)
```
---

# Reporting Section 

---

# Reporting Section

## Build the master event dataset
```{r build-master-event-dataset, message=FALSE, warning=FALSE}
enc_core_reporting <- encounters_std %>%
  filter(!is.na(visit_date), visit_date <= DATA_LOCK) %>%
  distinct(participant_id, csn, visit_date, .keep_all = TRUE) %>%
  left_join(
    participants_std %>% select(participant_id, enrollment_date),
    by = "participant_id"
  ) %>%
  left_join(
    roster_key %>% select(participant_id, site, tx_group, visit_date_3m, visit_date_6m),
    by = "participant_id"
  ) %>%
  mutate(
    patient_class = str_squish(patient_class),
    encounter_type = str_squish(encounter_type),
    study_bucket = assign_study_bucket(visit_date, enrollment_date, visit_date_3m, visit_date_6m),
    study_bucket = factor(study_bucket, levels = study_bucket_levels)
  )

ip_enc_reporting <- enc_core_reporting %>%
  filter(patient_class %in% ip_classes_all) %>%
  select(participant_id, csn, ip_date = visit_date)

ed_or_hosp_reporting <- enc_core_reporting %>%
  filter(patient_class %in% ed_classes | encounter_type == "Hospital Encounter") %>%
  transmute(participant_id, csn, ed_date = visit_date)

admission_flags_reporting <- ed_or_hosp_reporting %>%
  left_join(ip_enc_reporting, by = c("participant_id", "csn")) %>%
  group_by(participant_id, csn, ed_date) %>%
  summarise(
    admitted_same_csn = any(!is.na(ip_date)),
    admitted_within_1d = any(!is.na(ip_date) & ip_date >= ed_date & ip_date <= ed_date + days(1)),
    admitted = admitted_same_csn | admitted_within_1d,
    .groups = "drop"
  )

enc_dx_long_reporting <- enc_core_reporting %>%
  select(participant_id, csn, visit_date, diagnoses_raw) %>%
  mutate(icd_list = extract_icd10_from_diagnoses_raw(diagnoses_raw)) %>%
  unnest(icd_list, keep_empty = FALSE) %>%
  rename(icd10_raw = icd_list) %>%
  mutate(icd10 = clean_icd10(icd10_raw)) %>%
  filter(!is.na(icd10))

event_master <- enc_core_reporting %>%
  left_join(
    enc_dx_long_reporting %>%
      group_by(participant_id, csn, visit_date) %>%
      summarise(
        has_ideation = any(is_suicidal_ideation(icd10), na.rm = TRUE),
        has_attempt = any(is_suicide_attempt_code(icd10), na.rm = TRUE),
        has_selfharm_mech = any(is_intentional_self_harm_or_attempt(icd10), na.rm = TRUE),
        has_death_code = any(is_death_code(icd10), na.rm = TRUE),
        attempt_codes = paste(sort(unique(icd10[is_suicide_attempt_code(icd10)])), collapse = ", "),
        selfharm_codes = paste(sort(unique(icd10[is_intentional_self_harm_or_attempt(icd10)])), collapse = ", "),
        death_codes = paste(sort(unique(icd10[is_death_code(icd10)])), collapse = ", "),
        .groups = "drop"
      ),
    by = c("participant_id", "csn", "visit_date")
  ) %>%
  left_join(
    admission_flags_reporting,
    by = c("participant_id", "csn", "visit_date" = "ed_date")
  ) %>%
  mutate(
    admitted = coalesce(admitted, FALSE),
    has_ideation = coalesce(has_ideation, FALSE),
    has_attempt = coalesce(has_attempt, FALSE),
    has_selfharm_mech = coalesce(has_selfharm_mech, FALSE),
    has_death_code = coalesce(has_death_code, FALSE),
    is_psych_inpatient = patient_class %in% psych_ip_classes,
    is_any_inpatient = patient_class %in% ip_classes_all,
    is_ed_or_hosp = patient_class %in% ed_classes | encounter_type == "Hospital Encounter",
    event_detail = case_when(
      has_attempt ~ "Suicide Attempts",
      !has_attempt & has_selfharm_mech & (is_any_inpatient | (is_ed_or_hosp & admitted)) ~
        "Non-suicidal self-injury that results in an ED visit or hospitalization",
      !has_attempt & has_selfharm_mech ~
        "Non-suicidal self-injury that does not result in an ED visit or hospitalization",
      TRUE ~ NA_character_
    ),
    event_class = case_when(
      event_detail %in% c(
        "Suicide Attempts",
        "Non-suicidal self-injury that results in an ED visit or hospitalization"
      ) ~ "SAE",
      event_detail == "Non-suicidal self-injury that does not result in an ED visit or hospitalization" ~ "AE",
      TRUE ~ NA_character_
    ),
    week_in_study = if_else(
      !is.na(enrollment_date) & !is.na(visit_date),
      as.integer(floor(as.numeric(difftime(visit_date, enrollment_date, units = "days")) / 7)),
      NA_integer_
    )
  )

event_master %>%
  count(event_class, event_detail, sort = TRUE)
```

## Weekly/monthly regular tables
```{r regular-report-functions, message=FALSE, warning=FALSE}
study_bucket_levels_regular <- study_bucket_levels[study_bucket_levels != "Unassigned"]

add_missing_site_cols <- function(df, cols) {
  for (nm in cols) {
    if (!nm %in% names(df)) {
      df[[nm]] <- 0L
    }
  }
  df
}

make_regular_wide_table <- function(events_df, periods_df, metric_type = c("encounters", "participants"), event_type = c("SAE", "AE")) {
  metric_type <- match.arg(metric_type)
  event_type <- match.arg(event_type)

  base_df <- events_df %>%
    filter(!is.na(event_class), study_bucket != "Unassigned", event_class == event_type) %>%
    mutate(
      site = case_when(
        site %in% c("Harlem", "Kings") ~ site,
        TRUE ~ "Unknown"
      )
    )

  if (metric_type == "encounters") {
    base_df <- base_df %>%
      select(participant_id, csn, visit_date, study_bucket, site) %>%
      distinct()
  } else {
    base_df <- base_df %>%
      select(participant_id, visit_date, study_bucket, site) %>%
      distinct()
  }

  map_dfr(seq_len(nrow(periods_df)), function(i) {
    ps <- periods_df$period_start[i]
    pe <- periods_df$period_end[i]
    pl <- periods_df$period_label[i]

    if (metric_type == "encounters") {
      new_counts <- base_df %>%
        filter(visit_date >= ps, visit_date <= pe) %>%
        count(study_bucket, site, name = "n_new") %>%
        bind_rows(
          base_df %>%
            filter(visit_date >= ps, visit_date <= pe) %>%
            mutate(site = "Total") %>%
            count(study_bucket, site, name = "n_new")
        ) %>%
        group_by(study_bucket, site) %>%
        summarise(n_new = sum(n_new), .groups = "drop")

      cumulative_counts <- base_df %>%
        count(study_bucket, site, name = "n_cumulative") %>%
        bind_rows(
          base_df %>%
            mutate(site = "Total") %>%
            count(study_bucket, site, name = "n_cumulative")
        ) %>%
        group_by(study_bucket, site) %>%
        summarise(n_cumulative = sum(n_cumulative), .groups = "drop")
    } else {
      new_counts <- base_df %>%
        filter(visit_date >= ps, visit_date <= pe) %>%
        distinct(participant_id, study_bucket, site) %>%
        count(study_bucket, site, name = "n_new") %>%
        bind_rows(
          base_df %>%
            filter(visit_date >= ps, visit_date <= pe) %>%
            mutate(site = "Total") %>%
            distinct(participant_id, study_bucket, site) %>%
            count(study_bucket, site, name = "n_new")
        ) %>%
        group_by(study_bucket, site) %>%
        summarise(n_new = sum(n_new), .groups = "drop")

      cumulative_counts <- base_df %>%
        distinct(participant_id, study_bucket, site) %>%
        count(study_bucket, site, name = "n_cumulative") %>%
        bind_rows(
          base_df %>%
            mutate(site = "Total") %>%
            distinct(participant_id, study_bucket, site) %>%
            count(study_bucket, site, name = "n_cumulative")
        ) %>%
        group_by(study_bucket, site) %>%
        summarise(n_cumulative = sum(n_cumulative), .groups = "drop")
    }

    new_wide <- new_counts %>%
      pivot_wider(
        names_from = site,
        values_from = n_new,
        values_fill = 0,
        names_prefix = "new_"
      ) %>%
      add_missing_site_cols(c("new_Harlem", "new_Kings", "new_Total"))

    cum_wide <- cumulative_counts %>%
      pivot_wider(
        names_from = site,
        values_from = n_cumulative,
        values_fill = 0,
        names_prefix = "cum_"
      ) %>%
      add_missing_site_cols(c("cum_Harlem", "cum_Kings", "cum_Total"))

    tibble(
      study_bucket = factor(study_bucket_levels_regular, levels = study_bucket_levels_regular)
    ) %>%
      left_join(new_wide, by = "study_bucket") %>%
      left_join(cum_wide, by = "study_bucket") %>%
      mutate(
        period_label = pl,
        metric_type = metric_type,
        event_class = event_type,
        new_Harlem = coalesce(new_Harlem, 0L),
        cum_Harlem = coalesce(cum_Harlem, 0L),
        new_Kings  = coalesce(new_Kings, 0L),
        cum_Kings  = coalesce(cum_Kings, 0L),
        new_Total  = coalesce(new_Total, 0L),
        cum_Total  = coalesce(cum_Total, 0L)
      ) %>%
      select(
        period_label,
        metric_type,
        event_class,
        study_bucket,
        new_Harlem,
        cum_Harlem,
        new_Kings,
        cum_Kings,
        new_Total,
        cum_Total
      )
  })
}

weekly_monthly_encounter_sae <- make_regular_wide_table(
  event_master, periods_tbl, metric_type = "encounters", event_type = "SAE"
)

weekly_monthly_encounter_ae <- make_regular_wide_table(
  event_master, periods_tbl, metric_type = "encounters", event_type = "AE"
)

weekly_monthly_participant_sae <- make_regular_wide_table(
  event_master, periods_tbl, metric_type = "participants", event_type = "SAE"
)

weekly_monthly_participant_ae <- make_regular_wide_table(
  event_master, periods_tbl, metric_type = "participants", event_type = "AE"
)
```

```{r regular-report-build-gts, message=FALSE, warning=FALSE}
make_weekly_gt <- function(df, week_label, metric_label, event_label) {
  df %>%
    filter(period_label == week_label) %>%
    select(
      `Study Bucket` = study_bucket,
      `Harlem New` = new_Harlem,
      `Harlem Cumulative` = cum_Harlem,
      `Kings New` = new_Kings,
      `Kings Cumulative` = cum_Kings,
      `Total New` = new_Total,
      `Total Cumulative` = cum_Total
    ) %>%
    gt() %>%
    tab_header(
      title = md(paste0("**", event_label, " — ", metric_label, "**")),
      subtitle = md(paste0("**Week:** ", week_label))
    ) %>%
    tab_spanner(
      label = "Harlem",
      columns = c(`Harlem New`, `Harlem Cumulative`)
    ) %>%
    tab_spanner(
      label = "Kings",
      columns = c(`Kings New`, `Kings Cumulative`)
    ) %>%
    tab_spanner(
      label = "Total",
      columns = c(`Total New`, `Total Cumulative`)
    ) %>%
    cols_label(
      `Harlem New` = "New",
      `Harlem Cumulative` = "Cumulative",
      `Kings New` = "New",
      `Kings Cumulative` = "Cumulative",
      `Total New` = "New",
      `Total Cumulative` = "Cumulative"
    ) %>%
    cols_align(
      align = "center",
      columns = c(`Harlem New`, `Harlem Cumulative`, `Kings New`, `Kings Cumulative`, `Total New`, `Total Cumulative`)
    ) %>%
    fmt_number(
      columns = c(`Harlem New`, `Harlem Cumulative`, `Kings New`, `Kings Cumulative`, `Total New`, `Total Cumulative`),
      decimals = 0
    ) %>%
    tab_options(
      table.width = pct(100),
      data_row.padding = px(4)
    )
}

regular_report_gts <- list()

if (SHOW_REGULAR_AE_SAE_TABLES && REPORT_MODE %in% c("weekly", "monthly")) {
  for (p in unique(periods_tbl$period_label)) {
    regular_report_gts[[paste0(p, "_enc_sae")]] <- make_weekly_gt(
      weekly_monthly_encounter_sae, p, "Unique Encounters / Events", "SAE"
    )
    regular_report_gts[[paste0(p, "_enc_ae")]] <- make_weekly_gt(
      weekly_monthly_encounter_ae, p, "Unique Encounters / Events", "AE"
    )
    regular_report_gts[[paste0(p, "_pt_sae")]] <- make_weekly_gt(
      weekly_monthly_participant_sae, p, "Unique Participants", "SAE"
    )
    regular_report_gts[[paste0(p, "_pt_ae")]] <- make_weekly_gt(
      weekly_monthly_participant_ae, p, "Unique Participants", "AE"
    )
  }
}
```

```{r regular-report-output, warning=FALSE, message=FALSE, echo=FALSE}
# ========================= RUN REGULAR REPORT TABLES =======================

emit_gt <- function(x) {
  if (inherits(x, "gt_tbl")) {
    print(x)
  }
}

if (exists("regular_report_gts")) {
  for (g in regular_report_gts) emit_gt(g)
}
```

## DSMB Tables 
```{r dsmb-4-1, message=FALSE, warning=FALSE}
dsmb_events <- event_master %>%
  filter(!is.na(event_class), visit_date <= DATA_LOCK)

randomized_subjects <- roster_key %>%
  filter(tx_group %in% c("Control", "TX")) %>%
  distinct(participant_id, tx_group)

dsmb_4_1 <- randomized_subjects %>%
  left_join(
    dsmb_events %>%
      filter(event_class == "SAE") %>%
      distinct(participant_id) %>%
      mutate(has_sae = TRUE),
    by = "participant_id"
  ) %>%
  mutate(has_sae = coalesce(has_sae, FALSE)) %>%
  group_by(tx_group) %>%
  summarise(
    n_randomized_subjects = n_distinct(participant_id),
    n_randomized_subjects_with_sae = sum(has_sae),
    total_saes = sum(dsmb_events$event_class == "SAE" & dsmb_events$tx_group == first(tx_group), na.rm = TRUE),
    proportion_with_sae = 100 * n_randomized_subjects_with_sae / n_randomized_subjects,
    .groups = "drop"
  )

dsmb_4_1
```

```{r dsmb-4-2, message=FALSE, warning=FALSE}
dsmb_4_2 <- dsmb_events %>%
  filter(event_class == "SAE") %>%
  arrange(tx_group, visit_date, participant_id, csn) %>%
  group_by(tx_group) %>%
  mutate(sae_number = paste0("SAE-", str_pad(row_number(), 3, pad = "0"))) %>%
  ungroup() %>%
  transmute(
    `Treatment Group` = tx_group,
    `SAE #` = sae_number,
    `Subject ID` = participant_id,
    `Date of Event` = visit_date,
    `Week in Study` = week_in_study,
    `Date of last dose of blinded study medication` = NA_character_,
    `Relatedness to BLINDED study drug` = NA_character_,
    `Expected Y/N` = NA_character_,
    `Outcome` = NA_character_,
    `Description of Event` = event_detail
  )

dsmb_4_2
```

```{r dsmb-4-3, message=FALSE, warning=FALSE}
death_events <- event_master %>%
  filter(has_death_code, visit_date <= DATA_LOCK) %>%
  arrange(visit_date, participant_id, csn) %>%
  mutate(death_report_number = paste0("DR-", str_pad(row_number(), 3, pad = "0")))

dsmb_4_3 <- death_events %>%
  transmute(
    `DR #` = death_report_number,
    `Subject ID` = participant_id,
    `Treatment Group (A,B)` = tx_group,
    `Date of Death` = visit_date,
    `Week in Study` = week_in_study,
    `Date of last dose of BLINDED study medication` = NA_character_,
    `Relatedness to BLINDED study drug` = NA_character_,
    `Suicide Y/N` = if_else(has_attempt | has_ideation | has_selfharm_mech, "Y", "N"),
    `Description of Event` = if_else(
      death_codes != "",
      paste0("Provisional ICD-based death flag: ", death_codes),
      "Provisional ICD-based death flag"
    )
  )

dsmb_4_3
```

```{r dsmb-4-5, message=FALSE, warning=FALSE}
row_order_4_5 <- c(
  "Total SAEs",
  "Suicide Attempts",
  "Non-suicidal self-injury that results in an ED visit or hospitalization",
  "Total Self-harm AEs",
  "Non-suicidal self-injury that does not result in an ED visit or hospitalization"
)

ae_events_4_5 <- dsmb_events %>%
  filter(event_detail %in% c(
    "Suicide Attempts",
    "Non-suicidal self-injury that results in an ED visit or hospitalization",
    "Non-suicidal self-injury that does not result in an ED visit or hospitalization"
  )) %>%
  transmute(
    participant_id, csn, visit_date, site, tx_group, row = event_detail
  ) %>%
  distinct()

ae_events_4_5_with_totals <- bind_rows(
  ae_events_4_5,
  ae_events_4_5 %>%
    filter(row %in% c(
      "Suicide Attempts",
      "Non-suicidal self-injury that results in an ED visit or hospitalization"
    )) %>%
    mutate(row = "Total SAEs"),
  ae_events_4_5 %>%
    mutate(row = "Total Self-harm AEs")
) %>%
  distinct()

counts_long_4_5 <- ae_events_4_5_with_totals %>%
  mutate(col = case_when(
    site == "Harlem" & tx_group == "Control" ~ "Harlem - Control",
    site == "Harlem" & tx_group == "TX" ~ "Harlem - TX",
    site == "Kings"  & tx_group == "Control" ~ "Kings - Control",
    site == "Kings"  & tx_group == "TX" ~ "Kings - TX",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(col)) %>%
  count(row, col, name = "n") %>%
  complete(
    row = row_order_4_5,
    col = c("Harlem - Control", "Harlem - TX", "Kings - Control", "Kings - TX"),
    fill = list(n = 0L)
  )

cumulative_4_5 <- ae_events_4_5_with_totals %>%
  count(row, name = "Cumulative") %>%
  complete(row = row_order_4_5, fill = list(Cumulative = 0L))

dsmb_4_5 <- counts_long_4_5 %>%
  pivot_wider(names_from = col, values_from = n, values_fill = 0L) %>%
  left_join(cumulative_4_5, by = "row") %>%
  mutate(row = factor(row, levels = row_order_4_5)) %>%
  arrange(row) %>%
  rename(`# of AEs` = row) %>%
  select(
    `# of AEs`,
    Cumulative,
    `Harlem - Control`,
    `Harlem - TX`,
    `Kings - Control`,
    `Kings - TX`
  )

dsmb_4_5
```

```{r dsmb-4-6, message=FALSE, warning=FALSE}
dsmb_4_6 <- dsmb_events %>%
  filter(event_detail %in% c(
    "Suicide Attempts",
    "Non-suicidal self-injury that results in an ED visit or hospitalization",
    "Non-suicidal self-injury that does not result in an ED visit or hospitalization"
  )) %>%
  arrange(event_class, visit_date, participant_id, csn) %>%
  group_by(event_class) %>%
  mutate(
    event_number = row_number(),
    `SAE#` = if_else(event_class == "SAE", paste0("SAE-", str_pad(event_number, 3, pad = "0")), NA_character_),
    `AE#`  = if_else(event_class == "AE",  paste0("AE-",  str_pad(event_number, 3, pad = "0")), NA_character_)
  ) %>%
  ungroup() %>%
  transmute(
    `SAE#`,
    `AE#`,
    `TX Group` = tx_group,
    `Subject ID` = participant_id,
    `Date of Event` = visit_date,
    `Week in Study` = week_in_study,
    `Expected (Y/N)` = NA_character_,
    `Outcome` = NA_character_,
    `SAE type` = if_else(event_class == "SAE", event_detail, NA_character_),
    `AE type` = if_else(event_class == "AE", event_detail, NA_character_),
    `Method of Attempt` = case_when(
      attempt_codes != "" ~ attempt_codes,
      selfharm_codes != "" ~ selfharm_codes,
      TRUE ~ NA_character_
    ),
    `Was treatment received for attempt?` = if_else(
      event_detail == "Suicide Attempts",
      if_else(!is.na(procedures_raw) & str_squish(procedures_raw) != "", "Y", "N"),
      NA_character_
    ),
    `If no treatment, was this the most recent attempt?` = NA_character_
  )

dsmb_4_6
```

```{r dsmb-output, message=FALSE, warning=FALSE, results='asis'}
if (SHOW_DSMB && REPORT_MODE == "DSMB") {
  cat("\n\n# Section 4: Safety Data\n\n")

  cat("\n## 4.1 Proportion of Serious Adverse Events by Treatment Group\n\n")
  print(dsmb_4_1)

  cat("\n## 4.2 Serious Adverse Events Listing by Treatment Group\n\n")
  print(dsmb_4_2)

  cat("\n## 4.3 Death Reports\n\n")
  print(dsmb_4_3)

  cat("\n## 4.5 Number of Self-harm Adverse Events by Site and Treatment\n\n")
  print(dsmb_4_5)

  cat("\n## 4.6 Self-harm Reports\n\n")
  print(dsmb_4_6)
}
```

